A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-20 paper/main.tex
revise introduction (and abstract)

\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht; Werte würde ich eher runden }
\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e. the audio-only variant) as an addition to a large public functional brain imaging dataset (\href{www.studyforrest.org}{studyforrest.org}).
The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
Additionally for every word, we provide lemmatization, a simple
part-of-speech-tagging putting words into 15 grammatical categories, a detailed
part-of-speech tagging putting words into 43 grammatical categories, syntactic
dependencies within each sentence, and a semantic analysis based on word
embedding providing a 300-dimensional word vector.
This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
\end{abstract}

@@

Because naturalistic stimuli are multi-dimensional and their temporal structure
is usually unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data.  Nevertheless, model-driven methods, like a general
linear model (GLM), can be useful to investigate which specific stimulus
properties a brain region is responding to \citep{hamilton2018revolution}. For
example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.

For this publication, we annotated the exact onsets and offsets, and content of
sentences, single words, and phonemes spoken in the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description (i.e. an
audio-only variant of the movie)\citep{ForrestGumpDVD}.
% immediate reference not needed in the intro
%(see Table \ref{tab:overview} for an overview of the annotation's content).

fMRI data of participants watching the audio-visual movie \citep{hanke2016simultaneous} and listening to the audio-description \citep{hanke2014audiomovie} are the core data of the publicly available \textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% the following seems unrelated to the scope of the paper
%Additional fMRI data of this dataset include the perception of musical genres
%\citep{hanke2015musical}, and retinotopic mappings and localization of higher
%visual areas of the same participants \citep{sengupta2016extension}.
The annotation presented here facilitates modelling of hemodynamic brain responses
correlated with speech-related events in the two stimuli.
It extends already available annotations of portrayed emotions
\citep{labs2015portrayed}, perceived emotions \citep{lettieri2019emotionotopy},
as well as cuts and locations depicted in the movie
\citep{haeusler2016annotation}.  All annotations can be used in any study
focusing on other aspects of real-life cognition by serving as additional
confound measures describing key properties of major building blocks of the
stimulus.

\todo[inline]{this work seems to improve/replace previous work (in part), it is important to state that clearly and identify which pieces are involved => es ist implizit im Text, der von “exact onset \& offsets” und weiter unten von “preliminary annotations” gesprochen wird; keine Ahnung, ob man kommunizieren sollte, dass die preliminary Dinger mal auf github waren; war jedenfalls nicht offensichtlich, beworben o.ä.\\
If you want to take this question in a revision, I am OK with that. However,
the intro still doesn't say anything about WHY one would want to do "modelling of
hemodynamic brain responses correlated with speech-related events" other than
to discard speech as a confound. This seems like a massive underselling.}

@@

\section*{Conclusions}
\todo[inline]{the paper needs to serve a purpose.
One is, of course, to be documentation for the annotation.
Another is to attract people to use this work for their own studies.
I would even argue that this is the \textit{main} purpose, given that the annotation in itself represents to scientific progress.
The need to give an accurate assessment what this can be used for and what is problematic or impossible.
ATM this is the only statement in this regard:
'facilitates modelling of hemodynamic brain responses correlating with speech-related events' and the only indication of purpose is 'additional confound measures'.
I think this is incongruent with the amount of work and the level of detail of
this annotation; öööööhh, okay. Mir sind da jetzt über 2 Tage wenig Superlative eingefallen, die über den bisherigen Text hinausgehen; fehlt mir wohl die geeignete Perspektive}
% state what you think are the main conclusions that can be realistically drawn from the findings in the paper, taking care not to make claims that cannot be supported.
As an extension of the studoforrest dataset, we present an annotation of spoken language in the two hours lasting ``research cut'' of the audio-visual movie ``Forrest Gump'' and its temporally aligned audio-description.
We annotated the onset and offset of sentences, words and phonemes, and the corresponding speaker's identity.
An additional tagging of each word's linguistic features and the public nature of the dataset enable independent working groups to create sophisticated models of hemodynamic activity correlating with speech-related events in a naturalistic stimulus.
Results of our dataset validating analysis that we run as a proof of concept show that the annotation's content can indeed / in principle be used to isolate/track speech-related networks in the human brain under life-like conditions.

>>>>

\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht; Werte würde ich eher runden }
\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e. the audio-only variant) as an addition to a large public functional brain imaging dataset (\href{www.studyforrest.org}{studyforrest.org}).
The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
Additionally for every word, we provide lemmatization, a simple
part-of-speech-tagging putting words into 15 grammatical categories, a detailed
part-of-speech tagging putting words into 43 grammatical categories, syntactic
dependencies within each sentence, and a semantic analysis based on word
embeddings representing each word in a 300-dimensional semantic space.
This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
\end{abstract}

@@

% data-driven methods
Because naturalistic stimuli are multi-dimensional and their temporal structure
is usually unknown, data-driven methods like intersubject correlation
(ISC)\citep{hasson2004intersubject} or independent component analysis
(ICA)\citep{bartels2004chronoarchitecture} are often used to analyze
corresponding fMRI data. However, data-driven methods alone fall short of
pinpointing their results to specific, time-locked features of a stimulus
\citep{kauttonen2015optimizing}.
% model-driven methods
Model-driven methods, like a general linear model (GLM), can be useful to
investigate how hemodynamic brain responses in isolated regions correlate with
stimulus features. They can explain not just ``how'' the brain is responding to
a stimulus but also ``why'' \citep{hamilton2018revolution}.
% GLM: example studies
For example, studies using GLMs based on annotations of a stimulus' temporal
structure have elucidated how the brain responds to visual features of a movie
\citep{bartels2004mapping} or speech-related features of a narrative
\citep{rocca2019language}.

% We:
For this publication, we revised previous, preliminary annotations done by our
lab and now provide one single annotation with exact onsets/offsets and content
of each sentences, word and phonemes (see Table \ref{tab:overview} for an
overview) spoken in the audio-visual movie ``Forrest Gump''
\citep{ForrestGumpMovie} and its audio-description (i.e. an audio-only variant
of the movie)\citep{ForrestGumpDVD}.
% the studyforrest dataset
fMRI data of participants watching the audio-visual movie
\citep{hanke2016simultaneous} and listening to the audio-description
\citep{hanke2014audiomovie} are the core data of the publicly available
\textit{studyforrest} dataset (\href{www.studyforrest.org}{studyforrest.org}).
% why
This publication enables researchers to model time-locked hemodynamic brain
responses that correlate with different aspects of spoken occurring in a 2-hour
lasting naturalistic stimulus.
% extending previous non-speech annotations
The current annotation of speech extends already available annotations of
portrayed emotions \citep{labs2015portrayed}, perceived emotions
\citep{lettieri2019emotionotopy}, as well as cuts and locations depicted in the
movie \citep{haeusler2016annotation}. All annotations can be used in any study
focusing on aspects of real-life cognition by serving as additional confound
measures describing key properties of major building blocks of the stimulus.

\todo[inline]{Das “why one should model” ist jetzt drin; Frage an dich als
Datenanalyse-Pro: Man kann doch bestimmt auch data-driven methods irgendwie
“constrainen”, und die durch eine Annotation verbessern? Hast du da eine
Formulierung und/oder auch ein (high-level) Paper für mich zu dem Thema?}

@@

\section*{Conclusions}
\todo[inline]{the paper needs to serve a purpose.
One is, of course, to be documentation for the annotation.
Another is to attract people to use this work for their own studies.
I would even argue that this is the \textit{main} purpose, given that the annotation in itself represents to scientific progress.
The need to give an accurate assessment what this can be used for and what is problematic or impossible.
ATM this is the only statement in this regard:
'facilitates modeling of hemodynamic brain responses correlating with speech-related events' and the only indication of purpose is 'additional confound measures'.
I think this is incongruent with the amount of work and the level of detail of
this annotation; öööööhh, okay. Mir sind da jetzt über 2 Tage wenig Superlative eingefallen, die über den bisherigen Text hinausgehen; fehlt mir wohl die geeignete Perspektive}
% state what you think are the main conclusions that can be realistically drawn from the findings in the paper, taking care not to make claims that cannot be supported.
As an extension of the studoforrest dataset, we present an annotation of spoken language in the two hours lasting ``research cut'' of the audio-visual movie ``Forrest Gump'' and its temporally aligned audio-description.
We annotated the onset and offset of sentences, words and phonemes, and the corresponding speaker's identity.
An additional tagging of each word's linguistic features and the public nature of the dataset enable independent working groups to create sophisticated models of hemodynamic activity correlating with speech-related events in a naturalistic stimulus.
Results of our dataset validating analysis that we run as a proof of concept show that the annotation's content can indeed / in principle be used to isolate/track speech-related networks in the human brain under life-like conditions.
